My English activity log

### 2020-04-18 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
intro + CCL + bibilo + juqu'au 18/04

>>>>

* **31/03/2020** : I wathed "The Lord Of The Rings : The Return Of The King".

## Arpil

* **05/04/2020** : I watched a video about Hardy & Weinberg equilibrum https://www.youtube.com/watch?v=7S4WMwesMts.

* **18/04/2020** : I wathed e video about virus structure and reproduction https://www.youtube.com/watch?v=2--7fz9Fr_s.
